Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-04-07 paper.tex
Fixed discussion.

\subsection{Communication Performance}
We tested the communication with different data rates from 1 bit/s up to
1 kbit/s. As one can see in figure \ref{fig:transmission} the signal
strength is quite low after backscattering. So the problem appears, that
not all bits of the A/D converter are used. Hence a lot of quantization
noise is introduced. In other words more gain is needed. The
transmission shown in figure \ref{fig:transmission} was carried out with
the maximum gain of 50 dB, which is available with the in
\ref{sub:rtl2832} decribed tuner. So we got to the limits of the
\textit{RTL-SDR} at that point. We were able to achieve a range indoors
with 1 bit/s of a couple of meteres, but when we use a higher bitrate we
can only communicate over a range of a couple of decimeter and still
have a bit error ratio of approximately 40 \%. The communiction
experiment was also carried out outside closer to the tower. We could
not figure out any improvements going closer to the tower.  
\section{Discussion}
We are aware of the fact, that our communication system has to be improved until it is able to be used in allday technology. These are aspects, where fine tuning is necessary to enhance the performance:
\begin{itemize}
	\item Antennas: Different backscattering antennas have to be
tried out to find the one with the best results. The question is mainly
to which frequency the antenna has to be tuned (e.g. to the center of
the TV signal or more to the edge of it). Moreover the standard
\textit{RTL-SDR} antenna including the coaxial cable are of quite low
quality. The antenna is e.g. too short. 
	\item Receiver: Some fine tuning can be made when it comes to the filter coefficients of the different filters.
	\item Frame: The frame structure can be optimized to be able to correct errors (e.g. Hamming code).  
\end{itemize}   
To come to a conclusion one can say, that we were able
\begin{itemize}
	\item to show, that spectrum scanning over a huge band with sweeping is possible using the \textit{RTL-SDR}.
	\item to provide a heat map of TV signals in a mid-sized swedish city as well as the tools to create it.
	\item to show for the first time, that backscatter communication is possible with the \textit{RTL-SDR}.
\end{itemize}

>>>>

\subsection{Communication Performance}
We tested the communication with different data rates from 1 bit/s up to
1 kbit/s. As one can see in figure \ref{fig:transmission} the signal
strength is quite low after backscattering. So the problem appears, that
not all bits of the A/D converter are used. Hence a lot of quantization
noise is introduced. In other words more gain is needed. The
transmission shown in figure \ref{fig:transmission} was carried out with
the maximum gain of 50 dB, which is available with the in
\ref{sub:rtl2832} decribed tuner. So we got to the limits of the
\textit{RTL-SDR} at that point. We were able to achieve a range indoors
with 1 bit/s of a couple of meteres, but when we use a higher bitrate we
can only communicate over a range of a couple of decimeter and still
have a bit error ratio of approximately 40 \%. The communiction
experiment was also carried out outside closer to the tower. We could
not figure out any improvements going closer to the tower.  
\section{Discussion}
We are aware of the fact, that our communication system has to be improved until it is able to be used in allday technology. Different backscattering antennas have to be tried out to find the one with the best results. The question is mainly to which frequency the antenna has to be tuned (e.g. to the center of the TV signal or more to the edge of it). Moreover the standard \textit{RTL-SDR} antenna including the coaxial cable are of quite low quality. The antenna is e.g. too short. Hence a custom antenna would be benificial at this point as well. Moreover some fine tuning can be made when it comes to the filter coefficients of the different filters. Finally the frame structure can be optimized to be able to correct errors (e.g. Hamming code).

To come to a conclusion one can say, that we were able to show, that spectrum scanning over a huge band with sweeping is possible using the \textit{RTL-SDR}. Therupon we could provide a heat map of TV signals in a mid-sized swedish city as well as the tools to create it. And last but not least we have shown for the first time, that backscatter communication is possible with the \textit{RTL-SDR}.
